\bf\mftitle

### 2011-01-11 doc/jInfer/full/architecture/architecture.tex
3154619 Create documentation for jInfer architecture - desired section
3154619 Create documentation for jInfer architecture - minors

\documentclass[a4paper,10pt,oneside]{article}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{palatino}
\usepackage{listings}
\usepackage{textcomp}
\usepackage{upquote}

\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
%	backgroundcolor=\color{lbcolor},
	tabsize=2,
	rulecolor=,
	language=java,
        basicstyle=\small\ttfamily,
        basewidth=0.51em,
        upquote=true,
        aboveskip={1.5\baselineskip},
        columns=fixed,
        showstringspaces=false,
        extendedchars=true,
        breaklines=true,
%        prebreak =\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
 %       frame=single,
        showtabs=false,
        showspaces=false,
        showstringspaces=false,
        identifierstyle=\ttfamily,
%        keywordstyle=\color[rgb]{0,0,1},
%        commentstyle=\color[rgb]{0.133,0.545,0.133},
%        stringstyle=\color[rgb]{0.627,0.126,0.941},
}

@@

Regular expression is in fact $n$-ary tree, for example expression $(a, b, ((c | d), e), f)$ can be viewed as in fig. \ref{reg_tree}.
\begin{figure}
\caption{Example tree for regular expression $(a, b, ((c | d), e), f)$} \label{reg_tree}
\centering\includegraphics[scale=0.5]{reg_tree.eps}
\end{figure}
We implement this tree by member of \code{Regexp} class called \code{children}, which is of type \code{List<Regexp<T>>}.
List contains children of regexp in means of regexp tree.

@@

\subsection{Module interfaces}

>>>>

\documentclass[a4paper,10pt,oneside]{article}
\usepackage{epsfig}
\usepackage{color}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
%\usepackage{palatino}
\usepackage[T1]{fontenc}
\usepackage[sc]{mathpazo}
\linespread{1.05}

\usepackage{listings}
\usepackage{textcomp}
\usepackage{upquote}

\definecolor{listinggray}{gray}{0.9}
\definecolor{lbcolor}{rgb}{0.9,0.9,0.9}
\lstset{
%	backgroundcolor=\color{lbcolor},
	tabsize=2,
	rulecolor=,
	language=java,
        basicstyle=\small\ttfamily,
        basewidth=0.51em,
        upquote=true,
%        aboveskip={1.5\baselineskip},
        columns=fixed,
        showstringspaces=false,
        extendedchars=true,
        breaklines=true,
%        prebreak =\raisebox{0ex}[0ex][0ex]{\ensuremath{\hookleftarrow}},
 %       frame=single,
        showtabs=false,
        showspaces=false,
        showstringspaces=false,
%        identifierstyle=\ttfamily,
%        keywordstyle=\color[rgb]{0,0,1},
%        commentstyle=\color[rgb]{0.133,0.545,0.133},
%        stringstyle=\color[rgb]{0.627,0.126,0.941},
}

@@

Regular expression is in fact $n$-ary tree, for example expression $(a, b, ((c | d), e), f)$ can be viewed as in fig. \ref{reg_tree}.
\begin{figure}
\caption{Example tree for regular expression $(a, b, ((c | d), e), f)$} \label{reg_tree}
\centering\includegraphics[scale=0.5]{reg_tree.eps}
\end{figure}
We implement this tree by member of \code{Regexp} class called \code{children}, which is of type \code{List<Regexp<T>{}>}.
List contains children of regexp in means of regexp tree.

@@

\subsection{Something that will vektor declare priority}

\subsection{(Nondeterministic) Finite Automaton}
